### 2025-04-25 correlation.qmd
20250417 - diagnostic plots
20250425 - xi correlation coefficient

A scatterplot with best-fit line is in @fig-scatterplotWithBestFitLine.

@@

XICOR::xicor(
  player_stats_seasonal$height,
  player_stats_seasonal$fantasyPoints,
  pvalue = TRUE
)

set.seed(52242) # for reproducibility

XICOR::calculateXI(
  player_stats_seasonal$height,
  player_stats_seasonal$fantasyPoints)
```

>>>>

A [scatterplot](#sec-scatterplot) with best-fit line is in @fig-scatterplotWithBestFitLine.

@@

XICOR::xicor(
  player_stats_seasonal$height,
  player_stats_seasonal$fantasyPoints,
  method = "permutation",
  pvalue = TRUE
)
```
